Comparing software variability across and within fMRI analysis packages

### 2022-01-03 paper/paper.tex
camille on repro

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical results. For SPM, the files (as measured by checksums) were different but differences
were visually unnoticeable. For AFNI, the activation maps were similar
overall, however, differences were noticeable visually.
The observed differences remained small (see Supplemental Material~\ref{sec:supp-repro}), and might be due to the use of
GNU/Octave vs MATLAB in SPM, and of multithreading in AFNI. We performed visual quality control of the AFNI
and SPM results for each individual subject and confirmed that T1-weighted images were
correctly skull-stripped and registered to the MNI template.

>>>>

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical results \camille{It would be nice here to be more specific about how you checked that they were identical -- using a sha sum ? And maybe even insisting by using ``striclty identifical''. I think for different people in the community ``identical'' can mean different things}. For SPM, the files (as measured by checksums) were different but differences
were visually unnoticeable. For AFNI, the activation maps were similar
overall, however, differences were noticeable visually.
The observed differences remained small \camille{maybe also add ``and the overall patterns of activations were preseved''} (see Supplemental Material~\ref{sec:supp-repro}), and might be due to the use of
GNU/Octave vs MATLAB in SPM, and of multithreading in AFNI. We performed visual quality control of the AFNI
and SPM results for each individual subject and confirmed that T1-weighted images were
correctly skull-stripped and registered to the MNI template.
